ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-26 pyked.tex
added citation for WebPlotDigitizer
some edits to conclusions

Instead, such data is typically found in under-documented
comma-separated value files and Excel spreadsheets, or contained in PDF tables
rather than as supplementary material associated with a paper.
In the worst case, data is only available in figures and must be digitized by the
use of software such as WebPlotDigitizer.
\todo{give a citation here}
% I think we're already stirring the pot enough, no need to call out
% specific people
% \todo{call out specific examples of these...?}{}
These practices limit the wide use of the valuable, extensive experimental data
available in the literature. Frenklach~\autocite{Frenklach:2007bm} further explained the
benefits of standardized, widely available data for combustion.
In brief, much of combustion\slash chemical kinetics research drives towards the ultimate goal
of developing predictive kinetic models---and ultimately this depends on a community
infrastructure for data and methods.

@@

Recognizing that the community has a need for an open and standardized data
serialization format, in this paper we have presented the \ck{} data format for
describing measurements taken from fundamental combustion experiments. \ck{}
files are formatted using the YAML language and are plain-text, human- and
machine-readable, and easy to construct.

We have also presented a Python-based tool, \pk{}, for validating and working
with \ck{} files. \pk{} provides the reference implementation of the validator
for \ck{} files and utilizes several common packages from Python's scientific
computing community. \pk{} and \ck{} currently support ignition delay
measurements from rapid compression machines and shock tubes, including facility
specific effects from each type of experiment.

>>>>

Instead, such data is typically found in under-documented
comma-separated value files and Excel spreadsheets, or contained in PDF tables
rather than as supplementary material associated with a paper.
In the worst case, data is only available in figures and must be digitized by the
use of software such as WebPlotDigitizer~\autocite{WebPlotDigitizer}.
% I think we're already stirring the pot enough, no need to call out
% specific people
% \todo{call out specific examples of these...?}{}
These practices limit the wide use of the valuable, extensive experimental data
available in the literature. Frenklach~\autocite{Frenklach:2007bm} further explained the
benefits of standardized, widely available data for combustion.
In brief, much of combustion\slash chemical kinetics research drives towards the ultimate goal
of developing predictive kinetic models---and ultimately this depends on a community
infrastructure for data and methods.

@@

In this paper we presented the \ck{} data format for describing measurements
taken from fundamental combustion experiments, recognizing
that the community has a need for an open and standardized data serialization format.
\ck{} files are formatted using the YAML language and are plain-text, human- and
machine-readable, and easy to construct.

We also presented a Python-based tool, \pk{}, for validating and working
with \ck{} files. \pk{} provides the reference implementation of the validator
for \ck{} files and utilizes several common packages from Python's scientific
computing community. \pk{} and \ck{} currently support ignition delay
measurements from rapid compression machines and shock tubes, including
facility-specific effects from each type of experiment.
